Discovery of s-process stars in the LAMOST survey

### 2018-02-18 article/ms.tex
close to submit

\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.~R. Casey,$^{1,2}$
M.~T. Miles,$^{1}$
A.~J. Kemp,$^{1}$ 
A.~I. Karakas,$^{1}$\newauthor
A.~Y.~Q. Ho,$^{3}$
J.~C. Lattanzio,$^{1}$ and
K.~C. Schlaufman$^{4}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}
Stars with peculiar enhancements of carbon and heavy elements ($Z > 30$) are historically referred to as `Barium stars'. While this chemical abundance pattern can be explained by thermally pulsing asymptotic giant branch (AGB) stars, many so-called Barium stars have not evolved through the red giant phase and therefore cannot be AGB stars. These less-evolved stars are generally thought to have accreted mass from a more-evolved AGB companion. For this reason the frequency and properties of less-evolved Barium stars are uniquely informative on the binary fraction, AGB yields, mass transfer, and stellar evolution. Here we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST. Our sample includes; 257 `Barium stars' that show enhancement in both barium and strontium, 49 stars showing only significant barium enhancement, and 661 exhibiting only strontium enhancement. This sample constitutes the largest number of s-process enhanced stars ever discovered. We find up to 51 Barium stars exhibit some evidence of technetium from LAMOST spectra, and most (46/51) have $\log{g}>2$, which suggests they cannot be AGB stars and may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event. Most (178/257) Barium stars in our sample show strong carbon enhancement, consistent with the literature. However, despite previous claims indicating that Barium stars are preferentially enhanced in sodium due to the NeNa nucleosynthesis cycle occurring in massive AGB stars, only 5 ($<2$\,\%) of our Barium stars show any evidence of sodium enhancement. A comparison with AGB yields suggests that the majority of our sample are consistent with a bottom-heavy initial mass function. When binary properties become available from end-of-mission Gaia astrometry, this sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.
\end{abstract}

@@

Barium stars as first recognised by \citet{Bidelman1951}, are chemically unique objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun. Barium stars exist as either intrinsic or extrinsic objects; intrinsic Barium stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements are produced through the s-process and exist on the surface as the result of a thermal pulsing cycle. According to the mass-transfer hypothesis, extrinsic Barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (intrinsic Barium star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determines 85\% of all Barium stars are in binary systems and claims that those that appear singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small phase range as detailed by \citet{pourbaix2004}. For these reasons, the properties and occurrence rate of Barium stars are informative of the theoretical birth rate of AGB stars, the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,karakas12016}. Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass. These energy bursts drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, enrichment on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.,][]{busso2001}. The star contracts after dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.

Barium giants form within a metallicity-dependent initial mass range (approximately $0.8 - 8\,M_{\odot}$), with the minimum mass for core helium and carbon burning decreasing as metallicity decreases. The age of these stars vary considerably, with some as old as $\approx$12\,Gyr in metal-poor globular clusters. In contrast, metal-rich, young observable stars may only reach $\approx$100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}.

Many Barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. 
%These studies show that the stellar populations of Barium stars can be separated into two groups when considering their absolute luminosity, kinematic, and spatial properties. 
The relationship between Barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}. \citet{pereira2011} also concludes that metal-rich Barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. It remains necessary to establish known abundances of s-process elements in a greater sample of Barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and compare to AGB star yields at different masses and metallicities.

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} to identify 967 s-process candidates. In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis} we discuss the properties of our Barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}. This data-driven model was used to estimate stellar labels for 454,180 giant stars. We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars. Cross-validation experience shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are approximately comparable to the APOGEE uncertainties \citep{alam2015}.

\subsubsection{Candidate selection} \label{sec:cand}
The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. Specifically, we identified Barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively. A negative residual, as shown in a candidate Barium star in Figure \ref{fig:figure1}, illustrates an enhancement in \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\,\AA\, and 4077\,\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. Stars identified to just show high levels of barium (and not necessarily strontium) required enhancement at both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars just enhanced in strontium we looked for significant residuals at the 4554\,\AA\ and 4215\,\AA\ absorption lines.

We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process candidate; these included:

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process candidates including; 257 `Barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement, as listed in Table \ref{table:table1}.

For the remainder of this paper we restrict our analysis to the 257 classical `Barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of Barium stars. Nevertheless, this sample still constitutes the largest collection of Barium stars ever discovered \citep[e.g.,][]{decastro2016}.

@@

\begin{table*}
\centering
\caption{Table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} & Tc\\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55} & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  & \ding{55}   \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  & \ding{55}   \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}    \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55} & \ding{55}     \\ \hline
\end{tabular}
\end{adjustbox}
\end{table*}

\subsubsection{Enhancements due to sodium, technetium, and carbon}
We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 Barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select Barium stars enhanced in sodium, and required significant absorption in both features. Only 5/257 Barium stars met this criteria.

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found 51 Barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

\subsubsection{Abundances estimated from LAMOST spectra}
We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process candidates by synthesising spectra that would account for the observed flux residuals. We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively \citep{marcs,sme,vald,ispec}. We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citep{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$. Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.

\subsection{Follow-up observations with Magellan/MIKE}

\subsubsection{Observations and data reduction}
On the night of 07 January 2018 we acquired a high-resolution spectrum of two Barium star candidates (J09162834+0259348 and J08351472-0548480) using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile. Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude, with both candidates having $V \approx 12$. We observed both stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, providing a spectral resolution of ($\mathcal{R} \approx 28,000$). Exposure times of 100 seconds were sufficient to achieve a S/N ratio exceeding 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.

>>>>

\author[Brodie.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}\thanks{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
Andrew.~R. Casey,$^{1,2}$
Matthew T. Miles,$^{1}$
Alex J. Kemp,$^{1}$ \newauthor
Amanda I. Karakas,$^{1}$
Melissa Ness,
Kevin C. Schlaufman$^{4}$,
Anna Y.~Q. Ho,$^{3}$, \newauthor
and John C. Lattanzio,$^{1}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{abstract}

In this paper we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis. Finally, we validate our results using high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. Most of our barium stars ($69\%$) show strong carbon enhancements, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement. In contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies. A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star.

%The abundances of the slow neutron capture process (s-process) elements in stars are a measure of the nucleosyntheic processes that occur primarily in Asymptotic Giant Branch (AGB) stars. Due to their associated enrichment of the s-process element barium, stars with peculiar enhancements of carbon and heavy elements (Z > 30) are historically referred to as 'barium stars'.  Here, we present the discovery of 967 s-process candidates from 454,180 giant stars observed by LAMOST: this sample constitutes the largest number of s-process enhanced stars ever discovered. We identify these stars in the LAMOST sample by using a data-driven search approach on the spectra directly and then measure the s-process abundance enhancements directly using stellar synthesis. Finally, we validate our results using high resolution spectra of a number of candidates. Our sample includes; 257 'barium stars', that are enhanced in both barium and strontium, 49 stars with significant barium enhancement only, and 661 stars which exhibit strontium enhancement only. The unusual chemical abundance patterns of barium stars can be explained if these are in the AGB of stellar evolution. However, many barium stars  have not yet evolved through the red giant phase. Instead, these less evolved 'barium stars' are generally thought to have accreted mass from a more evolved AGB companion.  Our entire barium star stellar sample exists within temperature and luminosity ranges not enveloped by the AGB, which may indicate a recent ($<1\,\textrm{Myr}$) mass accretion event from an AGB companion. These less evolved stars are uniquely informative on the binary fraction, AGB yields, mass transfer and stellar evolution. A comparison with AGB yields suggests that the majority of our sample are consistent with Salpeter-like initial mass function, with pollution from a low mass AGB star. Most of our barium stars (put in percentage) show strong carbon enhancements, consistent with mass transfer from a low-mass AGB companion. Although, only 5 candidates ($<2$\,\%) show evidence of sodium enhancement, in contrast with previous claims of preferential sodium enhancement, we argue this may have been a selection bias in previous studies. When binary properties become available from end-of-mission Gaia astrometry, our sample of s-process stars will be critical in explaining mass transfer in binary systems and refining AGB yields across a range of masses and metallicities.

\end{abstract}

@@

Barium stars as first recognised by \citet{Bidelman1951}, are chemically unusual objects that exhibit envelopes with an overabundance of carbon and heavy elements (Z > 30) in comparison to the Sun. Barium enhanced stars exist as either intrinsic or extrinsic objects, stars intrinsically enhanced in barium and other s-process elements are known as AGB S stars. These stars are in the TP-AGB (thermally pulsing-asymptotic giant branch) phase, where the overabundance of both carbon and heavy elements produced through the slow neutron capture process and exist on the surface as the result of a thermal pulsing cycle. According to the mass-transfer hypothesis, extrinsic barium stars are a consequence of stellar wind accretion \citep{boffin1988,jorissen1992} or Roche-lobe overflow \citep{webbink1986}, and are within a binary system containing a previous TP-AGB companion star (AGB S star) in its final phase as a white dwarf \citep{bohm1980,bohm1984}. In fact, \citet{mcclure1983} determined 85\% of all barium stars are in binary systems and claimed that those that appear to be singular are actually pole-on, or highly eccentric binaries with significant radial velocity variations only occurring in a small ranges as detailed by \citet{pourbaix2004}. For these reasons, the properties and occurrence rate of barium stars are informative of the binary star fraction as a function of metallicity, the mass ratio of binary stars, as well as AGB yields across different masses and metallicities.

The slow neutron capture process (s-process), occurring in the interior of AGB stars, synthesises roughly half of all elements heavier than iron \citep[e.g.,][]{busso1999,travaglio2001,herwig2005,bisterzo2014,fishlock2014}. Late in the AGB phase, during the TP-AGB phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the mass of the H-exhausted core. These energy bursts drive a convective zone that sweeps almost the entire region lying between the core and the He-shell, mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This phase of expansion and resulting inward movement called the third dredge up (TDU), and is theorised to occur after each thermal pulse. During the TP-AGB phase, surface enrichment in $^{12}$C and heavy elements produced by the s-process, is a result of the repeated inward extensions of TDU \citep[e.g.,][]{busso2001}. The star contracts post dredge up and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times, and its frequency is dependent on the initial mass, composition, and mass-loss rate of the star.

Barium giants can form within a metallicity-dependent initial mass range of approximately $0.8 - 8\,M_{\odot}$. The minimum mass for these giants is defined by the mass needed for core helium and carbon burning, which decrease as metallicity decreases. The age of these stars vary considerably, with some as old as $\approx$ 12\,Gyr in metal-poor globular clusters. Metal poor stars enhanced in barium are defined in the literature as CH stars. In contrast, metal-rich, less massive stars may reach ages of $\approx$ 100Myr, this includes stars that are at the core carbon burning limit or very close to it \citep[e.g.,][]{whitelock2013}. Furthermore, metal rich stars enhanced in barium are defined in the literature as Bariu stars.

Many barium stars have been discovered in the disk and halo of the Milky Way \citep{gomez1997,mennessier1997}. In \citet{pereira2011} it is concluded that metal-rich barium stars share similar kinematics to other metal-rich and super metal-rich stars already analysed, suggesting that they do not belong to the bulge population. It remains necessary to establish known abundances of s-process elements in a greater sample of barium stars in order to compare their birth rate to theoretical expectations \citep{han1995}, explore the binary fraction at different metallicities, and to compare to AGB star yields at different masses and metallicities.
%The relationship between barium stars in the halo \citep[e.g.,][]{junqueira2001,drake2008,pereira2009,allen2006} and metal-poor, yellow, symbiotic halo stars has been established by \citet{jorissen2005} and \citet{pereira2009}.

In this paper we analyse 454,180 giant stars from the second LAMOST data release \citep{luo2015} and identify 967 s-process candidates. In Section \ref{sec:methods} we describe the observations and candidate selection, as well as the analysis of high-resolution follow-up observations obtained for a few candidates. In Section \ref{sec:dis} we discuss the properties of our barium stars in context of existing literature. We provide concluding remarks in Section \ref{sec:con}.

\section{Methods} \label{sec:methods}
\subsection{LAMOST analysis}
\subsubsection{Data-driven analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 giant stars in common between LAMOST and the APOGEE survey \citep{ho2017}. This data-driven model was used to estimate stellar labels for 454,180 giant stars. We note that this sample is exclusively giant stars, implying that we would not identify dwarf s-process enhanced stars. Cross-validation experience shows that the typical uncertainties are about 70\,K in effective temperature $\rm T_{\rm eff}$, 0.1\,dex in surface gravity $\log{g}$, 0.1\,dex in metallicity [M/H], and 0.04\,dex in the $\alpha$-element abundance relative to overall metallicity [$\alpha$/M]. These uncertainties are comparable to the APOGEE uncertainties \citep{alam2015}.

\subsubsection{Candidate selection} \label{sec:cand}
The barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. Specifically, we identified barium stars by searching for \ion{Ba}{II} and \ion{Sr}{II} enhancement at the 4554\,\AA\ and 4077\,\AA\ wavelengths, respectively. A negative residual, as shown in a candidate barium star in Figure \ref{fig:figure1}, illustrates an enhancement in the \ion{Ba}{II} and \ion{Sr}{II} lines at 4554\,\AA\, and 4077\,\AA, respectively. These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data. Stars identified high levels of barium (and not necessarily strontium) required enhancement in both the 4554\,\AA\ and 4934\,\AA\ \ion{Ba}{II} resonance lines, and for stars exclusively enhanced in strontium we looked for significant residuals at the 4077\,\AA\ and 4215\,\AA\ absorption lines.

We used five filters that each spectrum, for each set of absorption lines, had to meet in order to be considered a s-process rich candidate; these included:

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must be $A < -0.05$.
\item Both amplitudes must be measured within 3$\sigma$ ($|A|/\sigma _A$ < 3).
\item The wavelength at each absorption line must be within 2\,\AA\ ($\lambda$ < 2).
\item The reduced $\chi^2$ from \emph{The Cannon} must be $\chi_r^2 < 3$.
\item And, the LAMOST spectra must have a signal-to-noise ratio of $S/N > 30\,\textrm{pixel}^{-1}$.
\end{enumerate}
In addition, a visual inspection was undertaken to exclude any results containing false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated 967 s-process rich candidates which are provided in Table \ref{table:table1} including; 257 `barium stars' enhanced in both barium and strontium, 49 stars exhibiting exclusively barium enhancement, and 661 exhibiting exclusively strontium enhancement.

For the remainder of this paper we restrict our analysis to the 257 classical `barium stars' stars that show enhancement in both barium and strontium. While the 49 or 661 stars with only barium or strontium enhancements (respectively) may also be bonafide barium stars, there may be other explanations for their chemical abundance pattern \citep[e.g.,][]{maiorca2011}, and so we restrict our inferences to a `gold sample' of barium stars. Nevertheless, this sample still constitutes the largest collection of barium stars ever discovered, with the next sample of significant size containing 182 barium stars \citep[e.g.,][]{decastro2016}.

@@

\begin{table*}
\centering
\caption{Properties of 967 s-process candidates, the table is available online in its entirety. Here we show a portion to demonstrate its style and content.}
\label{table:table1}
\begin{adjustbox}{width=1\textwidth}
\begin{tabular}{@{}|l|l|c|c|c|c|c|c|c|c|c|c|c|c|c|@{}}
\toprule
2MASSID             & R.~A.         & Dec.        & $v_{r}$ & S/N & $\rm T_{\rm eff}$ & $\log{g}$ & [Fe/H] & [$\alpha$/Fe] & $\chi_r^2$ & [Ba/Fe] & [Sr/Fe] & \ion{Ba}{II} & \ion{Sr}{II} &  \ion{Ba}{II} \& \ion{Sr}{II} \\
& (J2000) & (J2000) & (km\,s$^{-1}$) & (pixel$^{-1}$) & (K)  \\ \midrule
J000019.26+501444.8 & 00:00:19.27 & +50:14:44.9 & -3.9  & 49      & 4973         & 3.27         & 0.21         & 0.08             & 0.66               & 0.25        & 0.83        & \ding{55} & \ding{51}  & \ding{55}   \\
J000020.55+411348.1 & 00:00:20.56 & +41:13:48.2 & -28.2 & 32      & 4882         & 2.74         & -0.22        & 0.04             & 0.23               & -0.17       & 0.90        & \ding{55}& \ding{51}  & \ding{55}    \\
J000134.95+490743.2 & 00:01:34.96 & +49:07:43.2 & -42.3 & 72      & 5044         & 3.11         & -0.54        & 0.11             & 0.79               & 1.02        & 0.45        & \ding{55} & \ding{55} & \ding{51}  \\
J000258.09+410730.0 & 00:02:58.10 & +41:07:30.1 & -34.5 & 41      & 4697         & 2.57         & -0.22        & 0.12             & 0.98               & -0.10       & 0.80        & \ding{55} & \ding{51}  & \ding{55}  \\
J000403.80+160257.1 & 00:04:03.80 & +16:02:57.2 & -35.4 & 42      & 5200         & 3.40         & -0.41        & 0.09             & 0.33               & 0.92        & 0.52        & \ding{55} & \ding{55} & \ding{51}  \\
J000439.16+183350.3 & 00:04:39.17 & +18:33:50.4 & -38.7 & 31      & 4601         & 2.50         & 0.44         & 0.03             & 0.34               & -0.11       & 0.88        & \ding{55} & \ding{51}  & \ding{55}  \\
J000444.87+400402.1 & 00:04:44.88 & +40:04:02.1 & -94.7 & 53      & 4172         & 1.46         & -0.08        & 0.09             & 0.72               & 0.03        & 0.91        & \ding{55} & \ding{51}  & \ding{55}  \\
J000552.76+261849.3 & 00:05:52.76 & +26:18:49.4 & -22.5 & 73      & 4924         & 3.14         & -0.05        & 0.09             & 0.67               & 0.28        & 0.85        & \ding{55} & \ding{51}  & \ding{55}  \\
J000737.70+394055.5 & 00:07:37.70 & +39:40:55.6 & -31.5 & 33      & 4700         & 2.80         & -0.04        & 0.07             & 0.28               & -0.13       & 0.81        & \ding{55} & \ding{51}  & \ding{55}  \\ \hline
\end{tabular}
\end{adjustbox}
\end{table*}

\subsubsection{Enhancements due to sodium, technetium, and carbon}
Enhancements in sodium, technetium, and carbon are useful indicators when determining whether a stellar sample is populated by intrinsically enhanced AGB S stars, or polluted extrinsic barium stars. We performed an identical analysis to the process described in Section \ref{sec:cand} in order to identify sodium, technetium, or carbon enhancement in our sample of 257 barium stars. We used the sodium doublet lines at 5889\,\AA\ and 5895\,\AA\ to select barium stars enhanced in sodium, and required significant absorption in both features. Only 5/257 barium stars met this criteria.

For technetium enhancement we searched for significant residual deviations at 4049\,\AA, 4238\,\AA, 4262\,\AA, 4297\,\AA, and 5924\,\AA. These absorption lines are extremely weak, and would require a substantial amount of technetium before it would be visible in a high S/N LAMOST spectrum. We found that 51 barium stars exhibited some level of significant enhancement (based on the filters above) at a single technetium line, yet none showed enhancement at more than one technetium line. We note that the single enhancement near technetium for these 51 stars may be the consequence of data reduction/calibration artefacts, but we include details of which stars matched on technetium in Table \ref{table:table1} nonetheless.
Finally, for carbon enhancement we searched for significant deviations at the CH and G band near 4300\,\AA. We found 178/257 stars to show significant carbon enhancement (i.e., $[\textrm{C/Fe}] \gtrsim 0.5$).

\subsubsection{Abundances estimated from LAMOST spectra}
We estimated [Ba/Fe] and [Sr/Fe] abundance ratios for all s-process enhanced candidates by synthesising spectra that would account for the observed flux residuals. We assumed that absorption due to metals is captured by \emph{The Cannon} model, and deviations in flux at the 4554\,\AA\ \ion{Ba}{II} line and the 4077\,\AA\ \ion{Sr}{II} transition are solely due to enhancements in Ba and Sr, respectively \citep{marcs,sme,vald,ispec}. We adopted the stellar parameters ($T_{\rm eff}$, $\log{g}$, [Fe/H]) from \citet{ho2017}, and assume a microturbulence of $v_{mic} = 2\,{\rm km\,s}^{-1}$. Uncertainties in [Ba/Fe] and [Sr/Fe] from LAMOST are taken as the fitting error due to noise, added in quadrature with an adopted $0.2\,{\rm dex}$ systematic error floor.

\subsection{Dynamics}
We integrated galactic orbits for 21 barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}. Using the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}. And, it is also used to vary the scale mass and radius, of the nucleus and halo, respectively. We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction. All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk, indicating they do not originate from an unusual stellar event.

\section{Follow-up observations with Magellan/MIKE}
